Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-09 rnni_convexity.tex
Theorem caterpillar_convex induction basis

\begin{proof}
We prove this theorem by backwards induction on the length of a shortest caterpillar path $d_c(T,R) = l$ ($l$ is the induction parameter) between trees $T$ and $R$.
We saw in the proof of Lemma~\ref{lemma:caterpillar_dist=diameter} that the maximum possible value for $l$ is $\frac{(n-1)(n-2)}{2}$, which forms the induction basis.
Lemma~\ref{lemma:caterpillar_dist=diameter} also implies in this case that $d(T, R) = d_c(T, R)$, hence there is a caterpillar path between $T$ and $R$ of length $d(T, R)$.

>>>>

\begin{proof}
We prove this theorem by backward induction on the length of a shortest caterpillar path $d_c(T,R) = l$ ($l$ is the induction parameter) between trees $T$ and $R$.
The backward induction basis follows by Lemma~\ref{lemma:caterpillar_dist=diameter}, as the maximum possible value for $l$ is $\frac{(n-1)(n-2)}{2}$.
